\section*{Publications}
\href{https://scholar.google.de/citations?user=D6WVFSYAAAAJ}{\textbf{Google Scholar Profile}} (citations: 444 / h-index: 11 / i10-index: 12)
%-----------------------------------------------------------------------------%
\subsection*{Journal articles}
%-----------------------------------------------------------------------------%
\begin{dated}
	\item[in revision]
		Anna Czypionka and Sven Lauer, 
		\textbf{`\#Tall this week': experimental evidence for an false-implication account}, 
		in revision for resubmission at \textit{Language}.
	\item[in revision]
		Sven Lauer and Prerna Nadathur, 
		\href{http://sven-lauer.net/output/LauerNadathur-CausalSufficiency.pdf}{\textbf{Causal necessity, causal sufficiency, and the implications of causative verbs}}, 
		in revision for resubmission at {\it Glossa}, for the special issue \textit{The grammar of dispositions}, ed. by Fabienne Martin and Tillmann Pross.
	\item[2016]
		Cleo Condoravdi and Sven Lauer, 2016,
		\href{http://dx.doi.org/10.3765/sp.9.8}{\textbf{Anankastic conditionals are just conditionals}},
		\textit{Semantics and Pragmatics}, 9(8).
	\item[2014]
		Sven Lauer and Cleo Condoravdi, 2014,
		\href{http://web.stanford.edu/~cleoc/Pac-Phil-Quart-preprint.pdf}{\textbf{Preference-conditioned necessities: Detachment and practical reasoning}},
		\textit{Pacific Philosophical Quarterly}, 95(4), 584--621.
\end{dated}
%-----------------------------------------------------------------------------%
\subsection*{Articles in refereed collections}
%-----------------------------------------------------------------------------%
\begin{dated}
	\item[2012]
		Cleo Condoravdi and Sven Lauer, 2012,
		\href{http://www.cssp.cnrs.fr/eiss9/eiss9_condoravdi-and-lauer.pdf}{\textbf{Imperatives: Meaning and illocutionary force}}, 
		in C. Pin\~on (ed.) \textit{Empirical Issues in Syntax and Semantics 9, Papers from the Colloque de Syntaxe et S\'emantique \`a Paris 2011}, 
		37--58.
	\item[2012]
		Alex Djalali, Sven Lauer and Christopher Potts, 2012, 
		\href{https://web.stanford.edu/~cgpotts/papers/djalali-lauer-potts-ac2011.pdf}{\textbf{Corpus evidence for preference-driven interpretation}}, 
		in M. Aloni, V. Kimmelman, F. Roelofsen, G. Weidman Sassoon, K. Schulz, and M. Westera (eds.)
		\textit{Proceedings of the 18th Amsterdam Colloquium: Revised Selected Papers}, 
		150--159. Berlin: Springer.
	\item[2011]
		Alex Djalali, David Clausen, Sven Lauer, Karl Schultz, and Christopher Potts, 2011, 
		\href{http://semanticsarchive.net/Archive/zZiM2YwN/djalali_et_al.pdf}{\textbf{Modeling expert effects and common ground using questions under discussion}}, 
		in \textit{Building Representations of Common Ground with Intelligent Agents: Papers from the 2011 AAAI Fall Symposium}, 
		10--15, Association for the Advancement of Artificial Intelligence, Washington D.C.
\end{dated} 
%-----------------------------------------------------------------------------%
\subsection*{Proceedings of refereed conferences and workshops}
%-----------------------------------------------------------------------------%
\begin{dated}
	\item[2017]
		Sven Lauer, 
		\href{http://sven-lauer.net/output/Lauer-AC17-I-Believe.pdf}{\textbf{`I believe' in a ranking-theoretic analysis of `believe'}},
		Proceedings of the Twenty-First Amsterdam Colloquium, 
		Amsterdam, The Netherlands, p. 335--344.
	\item[2017]
		Cleo Condoravdi and Sven Lauer, 2017. 
		\href{http://sven-lauer.net/output/CondoravdiLauer-NELS47-conditional-imperatives.pdf}{\textbf{Conditional imperatives and endorsement}}, 
		Proceedings of NELS 47, p.~185--204.
	\item[in press]
		Sven Lauer and Prerna Nadathur, in press.
		\href{http://sven-lauer.net/output/LauerNadathur-SuB21-most.pdf}{\textbf{Quantified indicative conditionals and the relative reading of {\it most}}}, 
		\textit{Sinn und Bedeutung 21}.
	\item[2016]
		Sven Lauer, 2016.
		\href{http://journals.linguisticsociety.org/proceedings/index.php/SALT/article/view/26.980/3695}{\textbf{On the status of `Maximize Presupposition'}}, 
		\textit{Proceedings of Semantics and Linguistic Theory (SALT) 26}.
	\item[2015]
		Sven Lauer, 2015. 
		\href{http://sven-lauer.net/output/Lauer-AC15-performative-modals.pdf}{\textbf{Performative uses and the temporal interpretation of modals}}, 
		in T. Brochhagen, Floris Roelofsen and Nadine Theiler (eds.) 
		\textit{Proceedings of the 20th Amsterdam Colloquium}, 
		Amsterdam, The Netherlands.
	\item[2015]
		Sven Lauer, 2015.
		\href{http://sven-lauer.net/output/Lauer-SuB19-BiscuitsProvisos.pdf}{\textbf{Biscuits and provisos: Conveying unconditional information by conditional means}}, 
		in E. Csipak and H. Zeijlstra (eds.) 
		\textit{Proceedings of Sinn und Bedeutung 19}, G\"ottingen,
		p~357--374.
	\item[2014]
		Sven Lauer, 2014. 
		\href{https://sites.google.com/site/fepesslli2014/proceedings}{\textbf{Mandatory implicatures in Gricean pragmatics}}, 
		in J. Degen, M. Franke, and N. Goodman (eds.)
		\textit{Proceedings of the Formal \& Experimental Pragmatics Workshop}, T\"ubingen,
		p~21--28.
	\item[2012]
		Anna Chernilovskaya, Cleo Condoravdi and Sven Lauer, 2012.
		\href{http://www.lingref.com/cpp/wccfl/30/paper2809.pdf}{\textbf{On the discourse effects of {\it wh}-exclamatives}}, 
		in N. Arnett and R. Bennett (eds.) 
		\textit{Proceedings of the 30th West Coast Conference on Formal Linguistics (WCCFL)}, 
		Cascadilla Press, Somerville, MA, p.~109--119.
	\item[2012]
		Sven Lauer, 2012. 
		\href{http://www.sven-lauer.net/output/Lauer-SuB16-LooseTalk-paper.pdf}{\textbf{On the pragmatics of pragmatic slack}}, 
		in A. Aguilar, R. Nouwen and A. Chernilovskaya (eds.) 
		\textit{Proceedings of Sinn und Bedeutung 16}, MIT Working Papers in Linguistics, 
		Cambridge, MA, p.~389--402.
	\item[2011]
		Cleo Condoravdi and Sven Lauer, 2011.
		\href{http://universaar.uni-saarland.de/monographien/volltexte/2011/30/artikel/Condoravdi_Lauer_sub15.pdf}{\textbf{Performative verbs and performative acts}}, 
		in I. Reich (ed.) 
		\textit{Proceedings of Sinn und Bedeutung 15},
		 Universaar---Saarland Unversity Press, Saarbr\"ucken, Germany, p.~149--164.
\end{dated}
%---------------------------------------------------------------------------------------------%
\subsection*{Dissertation}
%---------------------------------------------------------------------------------------------%
\begin{dated}
	\item[2013]
	Lauer, Sven, 2013.
	\href{http://sven-lauer.net/output/Lauer-Dissertation-DynamicPragmatics.pdf}{\textbf{Towards a dynamic pragmatics}}, 
	Ph.D. dissertation, Stanford University.
\end{dated}
%---------------------------------------------------------------------------------------------%
\subsection*{Manuscripts and work in progress}
%---------------------------------------------------------------------------------------------%
\begin{dated}
	\item[2012]
		Lauer, Sven. 
		\href{http://www.sven-lauer.net/output/Lauer-irgend-algun.pdf}{\textbf{Some news on {\it irgend-} and {\it alg\'un}}}, 
		manuscript, Stanford University.
	\item[2010]
		Lauer, Sven. 
		\href{http://sven-lauer.net/output/Lauer-QP-causatives.pdf}{\textbf{Periphrastic causative verbs in English: What do they mean?}}, 
		manuscript, Stanford University.
	\item[2009]
		Lauer, Sven. 
		\href{http://sven-lauer.net/output/Lauer-EVER-free-relatives.pdf}{\textbf{Free relatives with `-ever': Meaning and use}}, 
		manuscript, Stanford University.
\end{dated}