\section*{Service}
%
\subsection*{Peer Review}
%   
\begin{dated}
	\item[2014--present]
		\textbf{Member of the Editorial Board}\\
		Semantics \& Pragmatics.
	\item[2013--present]
		\textbf{Reviewer} (journals)\\
		Linguistics \& Philosophy ($4\times$),
		Journal of Semantics ($6\times$),
		Semantics \& Pragmatics ($6\times$),
		Natural Language and Linguistic Theory,
		Glossa,
		Journal of Germanic Linguistics,
		Mind,
		Discourse Processes,
		Journal of Pragmatics.
	\item[2013--present]
		 \textbf{Reviewer} (conferences, \&c.)\\
		Sinn und Bedeutung,
		Semantics and Linguistic Theory, 
		Amsterdam Colloquium, 
		North East Linguistics Society (NELS), 
		Chicago Linguistics Society (CLS), 
		XPrag, 
		various workshops \& collections.
\end{dated}
%
\subsection*{Departmental Service and Committees}
%
\begin{dated}
	\item[2017--present]
		\textbf{Member of the Executive Committee}\\
		Zukunftskolleg, University of Konstanz (since November 2017).
	\item[2017--present]
		\textbf{Member of the faculty search committee} (English Linguistics/Phonology)\\
		Department of Linguistics, University of Konstanz.
	\item[2014--2016]
		\textbf{Fellow Representative to the Department of Linguistics}\\
	    Zukunftskolleg, University of Konstanz.
	\item[2009--2010]
		\textbf{Member of the colloquium committee}\\
		Department of Linguistics, Stanford University.
	\item[2008--2009]
		\textbf{Graduate Student Representative}\\
		Department of Linguistics, Stanford University.
	\item[2008--2009]
		\textbf{Member of the Graduate Curriculum Review committee}\\
		Department of Linguistics, Stanford University.
	\item[2007--2008]
		\textbf{Member of the social committee}\\
	    Department of Linguistics, Stanford University.
\end{dated}
%
\subsection*{Organization of Workshops and Working Groups}
\begin{dated}
	\item[2017]
		\textbf{Biscuit Conditionals}, workshop.\\
		\textit{Co-Organizer}, with Arno Goebel and Julia Zakkou, 
		University of Hamburg.
	\item[2017]
		\textbf{Questioning Speech Acts}, workshop.\\
		\textit{Co-Organizer}, with Regine Eckardt, 
		University of Konstanz.
	\item[2017]
		 \textbf{Modeling causal dependencies in formal semantics}\\
		 \textit{Organizer}, 
		 University of Konstanz.
	\item[2015] 
		\textbf{New work on modals, conditionals and evidentials}, workshop.\\
		\textit{Organizer}, 
		University of Konstanz.
	\item[2014--2016]
		\textbf{Foundations of Semantics}, working group and speaker series.\\
		\textit{Cofounder and co-organizer}, with Brendan Balcerak Jackson and Doris Penka,\\ 
		University of Konstanz.
	\item[2010]
		\textbf{Game Theory and Communication}, workshop.\\
 		\textit{Co-organizer}, with Allistair Isaac and Thomas Icard, 
 		Stanford University.
 	\item[2009]
	 	\textbf{Counterfactuals, Causality and Inertia} (N3C), workshop.\\
       	\textit{Organizer}, 
       	Stanford University.
     \item[2008--2010]
     	\textbf{Construction of Meaning}, workshop / speaker series.\\
		\textit{Co-Organizer}, with Beth Levin and Scott Grimm, 
		Stanford University.
	\item[2007--2011]
		\textbf{Formal Pragmatics}, working group.\\
		\textit{Founder and Organizer}, 
		Stanford University.
\end{dated}