\section*{Teaching and Advising}
\subsection*{Teaching}
\subsubsection*{University of Konstanz}
\begin{dated}
	\item[2017]
		\textbf{Semantics III: The semantics of conditional structures},
		MA seminar.
	\item[2017]
		\textbf{Einf\"uhrung in die Sprachwissenschaft} (Introduction to Linguistics), 
		with Doris Penka.
	\item[2014]
		\textbf{Semantik I (Introduction to Formal Semantics)}.
\end{dated}
%
\subsubsection*{University of G\"ottingen}
%
\begin{dated}
	\item[2016] \textbf{Introduction to English Linguistics}.
	\item[2016] \textbf{Seminar in pragmatics: Speech acts in discourse}.
\end{dated}
%
\subsubsection*{Stanford University}
\begin{dated}
	\item[2011] \textbf{Logic and Language Lab}.
\end{dated}
%
\subsubsection*{North-American Summer School in Logic, Language and Information}
\begin{dated}
	\item[2010] \textbf{Imperative Meaning in Context}, with Cleo Condoravdi.
\end{dated}
%
\subsection*{Advising and supervision}
\subsubsection*{Primary advisor}
\begin{dated}
	\item[in progress]
		\textbf{Sandy Ciroux},
		Ph.D. in Linguistics,
		University of Konstanz.
\end{dated}
\subsubsection*{Secondary Advisor}
\begin{dated}
	\item[in progress] 
		\textbf{Ronja Bruderhofer}, 
		M.A. Linguistics, 
		University of Konstanz.
		%Secondary advisor (`Zweitgutachter')
	\item[2017] 
		\textbf{Ricarda Katzenbach}, 
		M.A. Wirtschaftspädagogik, 
		University of Konstanz.\\
		{``{}`Ach, das war doch nur ironisch gemeint' --- Zur Produktions- und Rezeptionstheorie von Ironie''} (`Oh, I meant that ironically --- On the production and reception of verbal irony')
		%Secondary advisor (`Zweitgutachter')
	\item[2016--2017]
		\textbf{Jette Fortmann}, 
		B.A. Linguistics,
		University of Konstanz.\\
        {``Modalpartikeln in Nebens\"atzen'' (`Discourse particles in subordinate clauses')}
        %Secondary advisor (`Zweitgutachter').
    \item[2015]
    	\textbf{Helge Linnert}, 
    	B.A. Linguistics,
    	University of Konstanz.\\
        {``Floated numeral quantifiers: The view from Japanese''}
    \item[2014--2015]
    	\textbf{Charlotte Bertet}, 
    	M.A. Linguistics,
    	University of Konstanz.\\
        {``Reportive Subjunctive in German''}
\end{dated}
%
\subsection*{Teaching Assistantships}
%
\subsubsection*{Stanford University}
%
\begin{dated}
	\item[2011] \textbf{Introduction to Linguistic Meaning}. Instructor: Chris Potts.
	\item[2010] \textbf{Introduction to Linguistics}. Instructor: Vivienne Fong.
	\item[2008] \textbf{Introduction to Syntax}. Instructor: Tom Wasow.
\end{dated}
%
\subsubsection*{Universit\"at Osnabr\"uck}
%
\begin{dated}
	\item[2005]  
		\textbf{Introduction to Computational Linguistics}. 
		Instructors: Graham Katz and Stephan Evert.
	\item[2004]
		\textbf{Introduction to Linguistics}. 
		Instructor: Graham Katz.
	\item[2002]
		\textbf{Introduction to Computational Linguistics}. 
		Instructors: Peter Bosch and Sabine Reinhart.
\end{dated}